\documentclass{amsart} 
\usepackage{amssymb,latexsym,amsmath,amscd,graphics,amsthm,verbatim,url}
%\usepackage[margin = 3 cm]{geometry}


\theoremstyle{plain}
%Create a problem environment to type up the questions.
\newtheorem{problem}{Problem}
      
%Create an environment Solution where the students will write their solutions.
\newenvironment{solution}{\paragraph{\emph{Solution 1}.}}{\hfill$\square$}


%Create an environment for the second try if necessary.
\newenvironment{sectry}{\paragraph{\emph{Solution 2}.}}{\hfill$\square$}


\begin{document} 

\title[Homework 4]{Homework 4}
\author{My name is:  WRITE YOUR NAME HERE}  %Replace WRITE YOUR NAME HERE by your actual full name
\date{\today} 
\maketitle 

\begin{problem}
Which of the following is a negation for ``All discrete mathematics students are athletic?''  More than one answer may be correct.
\begin{enumerate}
\item There is a discrete mathematics student who is non athletic.
\item All discrete mathematics students are nonathletic.
\item There is an athletic person who is not a discrete mathematics students.
\item No discrete mathematics students are athletic.
\item Some discrete mathematics students are nonathletic.
\item No athletic people are discrete mathematics students.
\end{enumerate}
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}

\begin{problem}
Write a formal negation for each of the following statements.
\begin{enumerate}
\item $\forall$ string $s$, $s$ has at least one character.
\item $\forall$ computer $c$, $c$ has a CPU.
\item $\exists$ a movie $m$ such that $m$ is over $6$ hours long.
\item $\exists$ a band $b$ such that $b$ has won at least $10$ Grammy awards.
\end{enumerate}
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}

\begin{problem}
Write a negation of the statement
$$\forall\text{ real number }x, \text{ if }x>3 \text{ then } x^{2}>9. $$
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}


\begin{problem}
Let 
$$D = \{-48,-14,-8,0,1,3,16,23,26,32,36 \}. $$
Determine which of the following statements are true and which are false.  Provide counterexamples for the statements that are false.
\begin{enumerate}
\item $\forall x \in D$, if $x$ is odd then $x > 0$.
\item $\forall x \in D$, if $x$ is less than $0$ then $x$ is even.
\item $\forall x \in D$, if $x$ is even then $x \le 0$.
\item $\forall x \in D$, if the ones digit of $x$ is $2$, then the tens digit is $3$ or $4$.
\item $\forall x \in D$, if the ones digit of $x$ is $6$, then the tens digit is $1$ or $2$.
\end{enumerate}
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}

\begin{problem}
Let $D = E = \{-2,-1,0,1,2 \}$.  Write negations for each of the following statements and determine which is true, the given statement or its negation.
\begin{enumerate}
\item $\forall x \in D, \exists y \in E$ such that $x + y = 1$.
\item $\exists x \in D$ such that $\forall y \in E$, $x+y = -y$.
\item $\forall x \in D, \exists y \in E$ such that $xy \ge y$.
\item $\exists x \in D$ such that $\forall y \in E, x \le y$.
\end{enumerate}
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}

\begin{problem}
Consider the following statement:
$$\forall x \in \mathbb{R}, \exists y \in \mathbb{R} \text{ such that } x < y. $$
Write a new statement by interchanging the symbols $\forall$ and $\exists$, and state which is true:  the given statement, the version with interchanged quantifiers, neither, or both.
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}

\begin{problem}
Let $A = \{1,3,5,7,9 \}$, $B = \{3,6,9 \}$, and $C = \{2,4,6,8 \}$.  Find each of the following:
\begin{enumerate}
\item $A \cup B$
\item $A \cap B$
\item $A \cup C$
\item $A \cap C$
\item $A \smallsetminus B$
\item $B \smallsetminus A$
\item $B \cup C$
\item $B \cap C$
\end{enumerate}
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}

\begin{problem}
In each of the followings, answer the following questions:  Is $A \subseteq B$?  Is $B \subseteq A$?  Is either $A$ or $B$ a proper subset of the other?
\begin{enumerate}
\item $A = \{2, \{2 \}, (\sqrt{2})^{2} \}$, $B = \{2, \{2\},\{\{2\}\} \}$ 
\item $A = \{ \{ 1,2\}, \{2,3\}\}$, $B = \{1,2,3 \}$
\item $A = \{a,b,c \}$, $B = \{\{a\}, \{ b\}, \{c\} \}$
\item $A = \{\sqrt{16}, \{4 \} \}$, $B = \{4\}$,
\item $A = \{ x \in \mathbb{R} : \cos(x) \in \mathbb{Z} \}$, $B = \{x \in \mathbb{R} : \sin(x) \in \mathbb{Z} \}$
\end{enumerate}
\end{problem}


\end{document}



