\documentclass{amsart} 
\usepackage{amssymb,latexsym,amsmath,amscd,graphics,amsthm,verbatim,url}
%\usepackage[margin = 3 cm]{geometry}


\theoremstyle{plain}
%Create a problem environment to type up the questions.
\newtheorem{problem}{Problem}
      
%Create an environment Solution where the students will write their solutions.
\newenvironment{solution}{\paragraph{\emph{Solution 1}.}}{\hfill$\square$}


%Create an environment for the second try if necessary.
\newenvironment{sectry}{\paragraph{\emph{Solution 2}.}}{\hfill$\square$}


\begin{document} 

\title[Homework 9]{Homework 9}
\author{My name is:  WRITE YOUR NAME HERE}  %Replace WRITE YOUR NAME HERE by your actual full name
\date{\today} 
\maketitle 

\begin{problem}
For each of the first five problems of Homework 8, tell me if the function is invertible, and why.  If yes, give me its inverse.
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}

\begin{problem}
Let $f:A \rightarrow B$ be a function and assume it is invertible, so that we can talk about its inverse $f^{-1}:B \rightarrow A$.  Give an argument that explains why $f^{-1}$ itself is invertible.  What is $(f^{-1})^{-1}$?
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}

\begin{problem}
Consider the function $f:\mathbb{R}_{\le 0} \rightarrow \mathbb{R}_{\ge 0}$ given by $x \mapsto f(x) = x^{2}$.  
\begin{enumerate}
\item Sketch the graph of this function.
\item Is $f$ invertible?  Explain carefully.
\item If you answered yes to the last question, find its inverse.
\end{enumerate}
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}


\begin{problem}
True or False?  Given any set $X$ and given any functions $f,g,h:X \rightarrow X$, if $h$ is injective and $h \circ f = f \circ g$, then $f=g$.  Justify.
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}



\begin{problem}
Suppose that $f:X\rightarrow Y$ is an injective function.
\begin{enumerate}
\item Prove carefully that for every subset $A$ of $X$, $f^{-1}(f(A)) = A$.
\item Prove that for all subsets $A_{1}$ and $A_{2}$ in $X$, $f(A_{1} \cap A_{2}) = f(A_{1}) \cap f(A_{2})$.
\end{enumerate}
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}

\begin{problem}
Suppose $f:X \rightarrow Y$ and $g:Y \rightarrow Z$ are both bijective functions.  Prove that $g \circ f$ is invertible and that $(g \circ f)^{-1} = f^{-1} \circ g^{-1}$.
\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}

\begin{problem}
Let $f:X\rightarrow Y$ and $g:Y \rightarrow Z$ be two functions.  Is the following property true or false??  For every subset $C$ in $Z$, $(g \circ f)^{-1}(C) = f^{-1}(g^{-1}(C))$.  Justify your answer.

\end{problem}
\begin{solution}
% Write your solution here.
\end{solution}




\end{document}



